reOpt Data

### 2023-01-18 src/reopt.Rmd
normalized health impact metric

```{r}
Annual Renewable Electricity (%)
Lifecycle Total tons CO2
Internal Rate of Return (IRR) (%)
Lifecycle Costs of Health Emissions ($)

>>>>

```{r}
energy_production_metric <- reopt_data %>% 
  select(cbsa, city_msa, county, annual_renewable_electricity_percent_of_total) %>% 
  rename(annual_renewable_percent = annual_renewable_electricity_percent_of_total) %>% 
  # normalize data 
  mutate(normalized_annual_renewable = (annual_renewable_percent - min(annual_renewable_percent))/(max(annual_renewable_percent)-min(annual_renewable_percent)))

climate_impacts_metric <- reopt_data %>% 
  select(cbsa, city_msa, county, lifecycle_total_t_co2) %>% 
  # normalize total co2 
  mutate(normalized_total_co2 = (lifecycle_total_t_co2 - min(lifecycle_total_t_co2)) / (max(lifecycle_total_t_co2) - min(lifecycle_total_t_co2)))

financial_metric <- reopt_data %>% 
   select(cbsa, city_msa, county, irr) %>% 
  # normalize IRR
  mutate(normalized_irr = (irr - min(irr)) / (max(irr) - min(irr)))

health_impact_metric <- reopt_data  %>% 
   select(cbsa, city_msa, county, lifecycle_costs_of_health_emissions_difference_from_bau) %>% 
  rename(health_emissions_cost = lifecycle_costs_of_health_emissions_difference_from_bau) %>% 
  mutate(normalized_health_emission_cost = (health_emissions_cost - min(health_emissions_cost)) / (max(health_emissions_cost) - min(health_emissions_cost)))
